Quantifying the importance of an inference model in Bayesian phylogenetics

### 2020-03-26 supplement.tex
Updates from Overleaf
Remove the likelihood shape
Update figures

@@

The code used in this part of the article can be found at 
\url{https://github.com/richelbilderbeek/pirouette_example_30}.

@@

The code used in this part of the article can be found at 
\url{https://github.com/richelbilderbeek/pirouette_example_28}.

@@

The main example uses 6 taxa. Here, we show the same results as the main example,
except for a varying number of taxa.

The code used in this part of the article can be found at 
\url{https://github.com/richelbilderbeek/pirouette_example_28} (6 taxa, main example),
\url{https://github.com/richelbilderbeek/pirouette_example_32} (12 taxa),
\url{https://github.com/richelbilderbeek/pirouette_example_33} (24 taxa),
\url{https://github.com/richelbilderbeek/pirouette_example_41} (32 taxa),
\url{https://github.com/richelbilderbeek/pirouette_example_42} (40 taxa).

@@

The code used in this part of the article can be found at 
\url{https://github.com/richelbilderbeek/pirouette_example_19} (500 nucleotides),
\url{https://github.com/richelbilderbeek/pirouette_example_28} (1000 nucleotides, main example),
and \url{https://github.com/richelbilderbeek/pirouette_example_34} (2000 nucleotides).

@@

The code used in this part of the article can be found at 
\url{https://github.com/richelbilderbeek/pirouette_example_27}.

@@

The code used in this part of the article can be found at 
\url{https://github.com/richelbilderbeek/pirouette_example_22}.

@@

The code used in this part of the article can be found at 
\url{https://github.com/richelbilderbeek/pirouette_example_26}.

@@

Here we show the results of a \verb;pirouette; run on a dataset 
of 2 trees simulated under a diversity-dependent process. 
All the trees are simulated using the DDD package (\cite{DDD}). 
Our goal is to show how trees simulated by a process that is 
sensibly different from a standard tree prior will result in a 
significant divergence between true and twin distribution. 
To do so we set the simulation parameters (in this case: 
absolute speciation rate $\lambda_0 = 1.6$, 
extinction rate $\mu = 0.2$ and carrying capacity $K = 20$) 
in order to express clear characteristics of diversity dependence in the 
phylogenies. In fact, for a high speciation rate and a low carrying capacity, 
we expect trees to exhibit high unbalance, compared with trees generated 
by a standard birth-death model. 
We can measure how unbalanced is a tree using the $\gamma$ 
statistics (\cite{pybus2000testing}). For this reason, we choose to 
measure the error made by the inference process using the $\gamma$ error statistics, 
which is currently implemented in \verb;pirouette;.

The code used in this part of the article can be found at 
\url{https://github.com/richelbilderbeek/pirouette_example_23}
and took 120 hours in total.

@@

\begin{figure}[H]
  \includegraphics[width=\textwidth]{pirouette_example_23/likelihoods.png}
  \caption{Distribution of likelihoods, as well as which ones are picked}
\end{figure}

@@

The code used in this part of the article can be found at 
\url{https://github.com/richelbilderbeek/pirouette_example_18} and
\url{https://github.com/richelbilderbeek/pirouette_example_28}.

@@

The main example uses a mutation rate such that all nucleotides,
on average, mutate once over the history going from the
ancestral sequence at the crown to the alignments at the tips.
In this way, the alignment is expected to contain the maximum
amount of information.

Here, we show the same results, with the only difference that
the mutations rates are changed.
For a lower mutation rate, less mutations will be observed, thus
genetic information will be less, thus the inference is expected
to go worse, thus the errors are expected to increase.
For a lower mutation rate, more double-mutations will occur,
scrambling the alignments, resulting in less genetic information, 
thus the inference is expected to go worse, 
thus the errors are expected to increase.

The code used in this part of the article can be found at 
\url{https://github.com/richelbilderbeek/pirouette_example_35} (0.25 / crown age),
\url{https://github.com/richelbilderbeek/pirouette_example_36} (0.50 / crown age),
\url{https://github.com/richelbilderbeek/pirouette_example_37} (0.75 / crown age),
\url{https://github.com/richelbilderbeek/pirouette_example_28} (1.00 / crown age, main example),
\url{https://github.com/richelbilderbeek/pirouette_example_38} (1.25 / crown age),
\url{https://github.com/richelbilderbeek/pirouette_example_39} (1.50 / crown age),
\url{https://github.com/richelbilderbeek/pirouette_example_40} (2.00 / crown age),

>>>>

For all experiments, the intermediate results can all be downloaded 
from their respective websites.

@@

The code to reproduce this can be found at  
\url{https://github.com/richelbilderbeek/pirouette_example_30}.

@@

The code to reproduce this figure can be found at  
\url{https://github.com/richelbilderbeek/pirouette_example_28}.

@@

The main example uses 6 taxa. Here, we show the same results as the main example,
except for a varying number of taxa. We did so, by setting the DD model's
carrying capacity to the desired number of taxa.

The code to reproduce these figure can be found at  
\url{https://github.com/richelbilderbeek/pirouette_example_28} (6 taxa, main example),
\url{https://github.com/richelbilderbeek/pirouette_example_32} (12 taxa),
\url{https://github.com/richelbilderbeek/pirouette_example_33} (24 taxa),
\url{https://github.com/richelbilderbeek/pirouette_example_41} (32 taxa),
\url{https://github.com/richelbilderbeek/pirouette_example_42} (40 taxa).

@@

The code to reproduce these figures can be found at  
\url{https://github.com/richelbilderbeek/pirouette_example_19} (500 nucleotides),
\url{https://github.com/richelbilderbeek/pirouette_example_28} (1000 nucleotides, main example),
and \url{https://github.com/richelbilderbeek/pirouette_example_34} (2000 nucleotides).

@@

The code to reproduce this figure can be found at  
\url{https://github.com/richelbilderbeek/pirouette_example_27}.

@@

The code to reproduce this figure can be found at  
\url{https://github.com/richelbilderbeek/pirouette_example_22}.

@@

The code to reproduce this figure can be found at  
\url{https://github.com/richelbilderbeek/pirouette_example_26}.

@@

Here we show the results of a \verb;pirouette; run on a dataset 
of multiple DD trees that we selected for having a low, median
and high likelihood. In that way, we effectively selected for trees
that are rare, uncommon and common respectively.

The code to reproduce these figure can be found at  
\url{https://github.com/richelbilderbeek/pirouette_example_23}
and took 120 hours in total.

@@

@@

The code to reproduce this figure can be found at  
\url{https://github.com/richelbilderbeek/pirouette_example_18} and
\url{https://github.com/richelbilderbeek/pirouette_example_28}.

@@

The main example uses a mutation rate such that all nucleotides,
on average, mutate once over the history going from the
ancestral sequence at the crown to the alignments at the tips.
This value equals `1.0 / crown age`.
In this way, the alignment is expected to contain the maximum
amount of information.

Here, we show the same results for different mutation rates.

The code to reproduce this figure can be found at  
\url{https://github.com/richelbilderbeek/pirouette_example_35} (0.25 / crown age),
\url{https://github.com/richelbilderbeek/pirouette_example_36} (0.50 / crown age),
\url{https://github.com/richelbilderbeek/pirouette_example_37} (0.75 / crown age),
\url{https://github.com/richelbilderbeek/pirouette_example_28} (1.00 / crown age, main example),
\url{https://github.com/richelbilderbeek/pirouette_example_38} (1.25 / crown age),
\url{https://github.com/richelbilderbeek/pirouette_example_39} (1.50 / crown age),
\url{https://github.com/richelbilderbeek/pirouette_example_40} (2.00 / crown age),
